### 2014-10-30 transactions.tex
minor edits

\noindent $\cv_1$ and $\cv_2$ are the contracts on the corresponding
transactions. Our goal is to ensure that \cf{totalBalance} returns the result
obtained from a consistent snapshot of the object states.

>>>>

\noindent $\cv_1$ and $\cv_2$ are the contracts on the corresponding
transactions. The function \cf{classify} assigns the contracts
\emph{statically} to one of the transaction isolation levels offered by the
store; \cf{\$()} is meta-programming syntax for splicing the result into the
program. The \cf{atomically} construct invokes the enclosing operations at the
given isolation level $x$, ensuring that the effects of the operations are made
visible atomically. Our goal is to ensure that \cf{totalBalance} returns the
result obtained from a consistent snapshot of the object states.
